

This is the first of 10 WeBWorK based home work sets.  All
questions have equal weight.  Note that problems 11 and 12, 19 and 20,
and 21 and 22 are identical pairs with different numbers.  The purpose
of this is to encourage you to think in terms of a general approach to
the problem.  Future assignments will ask for answers in terms of
general parameters.

{\bf Due to Memorial Day, this assignment is due Wednesday, May 30, 7:00am.}


The maximum point count per problem is 24 points (send me a note with
your guess of how I came up with that funny number).  Most of the
questions are routine but some are a little more challenging.  You
should print the problems, do them at home or in another private
place, and then return to a computer and enter your answers.  Then
think about those problems for which your answers were incorrect.
Talk to each other, to the tutors, and don't hesitate to contact me if
you have any questions.  When you think you have the correct answers
return to a computer and enter them.  Getting the answers right may
take you several rounds of rethinking and entering them.  You have an
arbitrary number of attempts for each questions.  However, particularly the
more complicated problems may take you quite a while to figure out
correctly, so remember:

\bigskip\centerline{\large \bf Procrastination is hazardous}\bigskip

Significant effort has been made to make sure these problems make
sense and the answers provided to the computer system are correct.
Please let us know (using the feedback button)
if there are any discrepancies or your are sure
your answers are correct and the computer keeps refusing them. If you
are right the class will be informed and you will receive credit.

Peter Alfeld, JWB 127 or 236, 581-6842.

